Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-30 papers/LREC2020/background.tex
lrec camera ready, correcting 2 small issues identified by Carina

The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \word{dog}'', ``the white \word{dog} to the left'').\cs{rephrase}
Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be called by different names \cite{brown1958shall,murphy2004big}.

@@

In Computer Vision, object recognition is often modeled as a classification task where state-of-the-art systems identify objects by classifying them into thousands of different categories  \cite{googlenet,ILSVRC15}. 
Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology were automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}.\cs{double-check latter} 
Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.

@@

Our new collection, ManyNames, focusses on object names in isolation and is substantially more controlled than common L\&V datasets. This controlled collection procedure allowed us to elicit many names for the same object from different annotators, resulting in a dataset that is amenable to  studying systematically and on a large scale the core phenomena of object naming, viz. naming variation and preferences.\cs{rephrase}

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCOCO/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50,000 & 243,801 & 3,781,232 & 25,315 & 25,315 \\
    name vocabulary size &  5,004 &  10,423 &   105,441 &  1,061 &  7,970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    ratio of objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. name types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \caption{Overview statistics for different datasets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
\end{table*}

>>>>

The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \word{dog}'', ``the white \word{dog} to the left''). 
Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be called by different names \cite{brown1958shall,murphy2004big}.

@@

In Computer Vision, object recognition is often modeled as a classification task where state-of-the-art systems identify objects by classifying them into thousands of different categories  \cite{googlenet,ILSVRC15}. 
Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology were automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.

@@

Our new collection, ManyNames, focusses on object names in isolation and is substantially more controlled than common L\&V datasets. This controlled collection procedure allowed us to elicit many names for the same object from different annotators, resulting in a dataset that is amenable to  studying systematically and on a large scale the core phenomena of object naming, viz. naming variation and preferences.

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCOCO/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50,000 & 243,801 & 3,781,232 & 25,315 & 25,315 \\
    name vocabulary size &  5,004 &  10,423 &   105,441 &  1,061 &  7,970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    ratio of objects with \# types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. \# name types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \caption{Overview statistics for different datasets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
\end{table*}
